Prediction of 90-day mortality after Total Hip Arthroplasty: a simplified and externally validated model based on observational registry data from Sweden, England and Wales

### 2020-09-05 reports/article.Rmd
Revision submitted. Fix #47.

`r sprintf("%d [%s]", sum(df$death90), surv90d)` of the patients from SHAR died within 90 days and no one was censored before that. ~~The median age of patients who died was `r age_median` years (range `r age_range`; Table \@ref(tab:agedist).~~ Patients from ~~the~~ NJR had an unadjusted risk of 90-day mortality of `r njr_surv`. Further cohort characteristics are presented in Table \@ref(tab:tab1).

>>>>

`r sprintf("%d [%s]", sum(df$death90), surv90d)` of the patients from SHAR died within 90 days and no one was censored before that. ~~The median age of patients who died was `r age_median` years (range `r age_range`; Table \@ref(tab:agedist)).~~ Patients from ~~the~~ NJR had an unadjusted risk of 90-day mortality of `r njr_surv`. Further cohort characteristics are presented in Table \@ref(tab:tab1).
